\documentclass{article}

\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\fancyfoot[L]{IGDA IIIT-D}

\hypersetup{
    colorlinks=true,
    linkcolor=Apricot,
    urlcolor=Apricot,
    citecolor=Apricot,
    pdfauthor={Taraash},
    pdftitle={Final Project},
    pdfsubject={Game Development with Unreal Engine},
    pdfkeywords={Unreal Engine, Game Development, Final Project}
}

\title{Final Project}
\author{Game Development with Unreal Engine}
\date{}

\begin{document}
\maketitle

This document outlines the requirements, expectations, and submission format for your final team project.

\section{Pre-requisites}
\begin{enumerate}
    \item You must form teams of four.
    \item Work should be evenly distributed, please form a channel/thread on our Discord to keep everything convenient.
    \item Fill in the team details in the Google spreadsheet.
\end{enumerate}
\subsection{Links}
\begin{itemize}
\item \href{https://discord.gg/muZEEAHsg6}{The Discord Server invite}
\item \href{https://docs.google.com/spreadsheets/d/1uJ7tC7BC8lP6ygwYjTOuPb64RGZ_CsXMxxr8spKwdto/edit?usp=sharing}{The Google spreadsheet}
\end{itemize}

\section{The game}
\begin{enumerate}
    \item We recommend you take inspiration from an existing game, and recreate it in your style.
    \item It is recommended you target your game for a Windows PC, unless you've got a specific reason otherwise.
    \item Your game must have at least three playable levels. (Showing progression, variety, or difficulty.)
\end{enumerate}

\section{A few areas to keep in mind}
\begin{enumerate}
    \item \textbf{Aesthetics}: Does the game look good? Do the colors make sense? 
    \item \textbf{Level design}: Do the props make sense? Is it detailed, does it have a theme or a story?
    \item \textbf{Mechanics}: Can I do some cool stuff? Is it fun to play? 
    \item \textbf{Gameplay}: Is your game fun? 
    \item \textbf{UI}: Is the UI intuitive? Does it make sense? Is it easy to use?
    \item \textbf{Performance}: Does the game run well? Are there any performance issues?
    \item \textbf{Sound}: Does the game have sound? Is it appropriate? Does it add to the experience?
\end{enumerate}

\section{Submission}
\begin{enumerate}
    \item A summary of your ideation, work flow and distribution.
    \item A list of all mechanics made.
    \item A list of self-made assets (with the project specific files).
    \item A list of all third-party assets you used (with credits).
    \item A short write-up on any challenges faced and what you'd do differently.
    \item Project screenshots, a gameplay video and a playable build of your game.
\end{enumerate}

\section{Bonuses}
There are possible available bonuses which can help you make up for classes lost (remember, you need at least 80 hours for completion).
\begin{enumerate}
    \item Custom meshes
    \item Custom textures
    \item Additional tools you used (for example, Blender, Substance, ZBrush, etc.)
    \item Modular/reusable assets
\end{enumerate}
\emph{Note:} Bonuses are not mandatory, and we reserve the right to not give a bonus if we feel your work does not warrant it. We will discuss the number of hours you will get after taking a look at your work.

\end{document}